### 2016-06-27 methods.Rmd
ENH:  More response items.

\textcolor{blue}{Figure X provides a graphical overview of the proposed workflow.  The major components
include offline generation of symmetric multimodal templates, the creation of
feature images from the training data which are then used to model the statistical
prediction using a concatenated random forest framework.  Once these offline steps
are performed, a new, unsegmented subject can then be processed using the proposed pipeline.}

@@

@@

Supervised methodologies are uniquely characterized, in part, by the feature images that
are used to identify the regions of interest.  In Table 1, we provide a list and basic
categorization of the feature images used for the initial (i.e., Stage 1---more on the use
of multiple random forest stages below) segmentation of the WMHs.
In addition Figure 1 provides a representation of a set of feature images for a single
subject analyzed in this work.  Note that in this work we categorize the brain parenchyma
with seven labels:

@@

The T1 image is then processed via the ANTs brain
extraction and normal tissue segmentation pipelines [@Tustison:2014ab].
  The result is a mask delineating the brain parenchyma and probabilistic estimates of the
CSF, gray matter, white matter, deep gray matter, brain stem, and
cerebellum [@Avants:2011aa].  These provide the expertly annotated labels for the
first six tissue labels given above.  Tissue prior probability maps for segmentation
are from multi-model optimal symmetric shape/intensity templates [@Tustison:2015aa] created from the public MMRR data set  [@landman2011] (cf Figure 3).

<!--
![Canonical views of the mutlivariate, bilaterally symmetric template constructed
from the MMRR data set [@landman2011] (only shown are the FLAIR, T1, and T2 modalities---
the components relevant for this work).  Template construction is detailed in
[@Tustison:2015aa].  These images are important for specific intensity-based
features.](Figures/MMRR.png)
-->

>>>>

\textcolor{blue}{Figure 1 provides a graphical overview of the proposed workflow.  The major components
include offline generation of symmetric multimodal templates, the creation of
feature images from the training data which are then employed for statistical
prediction using a concatenated random forest framework.  This framework involves
the use of two random forest models where the outcome (i.e., the tissue
probability estimates) of the first RF model application,
which we denote as ``Stage1 '', is used as input (along with the original set of
feature images) to a refinement RF model segmentation which we denote as ``Stage 2''.
Once these offline steps
are performed, a new, unsegmented subject can then be processed using the proposed pipeline.}

@@

### Symmetric multi-modal templates

\textcolor{blue}{Following} [@Tustison:2014ab] \textcolor{blue}{and} [@Tustison:2015aa], \textcolor{blue}{optimally derived templates
serve for both brain tissue segmentation (for the derivation of tissue prior probability maps) and generation of asymmetry feature images.
For this work we use the multi-modal data available from the public MMRR data set}
[@landman2011]\textcolor{blue}{.  We used all 46 multi-modal acquisitions of that study to produce a multi-modal template according to the procedure described in} [@Avants:2010aa] \textcolor{blue}{which
results in a mean (in terms of both shape and intensity) multivariate template representing the entire cohort.  Mid-canonical slices of the FLAIR, T1, and T2 components are illustrated in Figure 2.}

<!--
![Canonical views of the mutlivariate, bilaterally symmetric template constructed
from the MMRR data set [@landman2011] (only shown are the FLAIR, T1, and T2 modalities---
the components relevant for this work).  Template construction is detailed in
[@Tustison:2015aa].  These images are important for specific asymmetry-based
features.](Figures/MMRR.png)

@@

Supervised methodologies are uniquely characterized, in part, by the feature images that
are used to identify the regions of interest.  In Table 1, we provide a list and basic
categorization of the feature images used for the initial (i.e., Stage 1---more on the use
of multiple random forest stages below) segmentation of the WMHs.
In addition Figure 3 provides a representation of a set of feature images for a single
subject analyzed in this work.  Note that in this work we categorize the brain parenchyma
with seven labels:

@@

The T1 image is then processed via the ANTs brain
extraction and normal tissue segmentation pipelines [@Tustison:2014ab].
  The result is a mask delineating the brain parenchyma and probabilistic estimates of the
CSF, gray matter, white matter, deep gray matter, brain stem, and
cerebellum [@Avants:2011aa].  These provide the expertly annotated labels for the
first six tissue labels given above.  Tissue prior probability maps for segmentation
are from multi-model optimal symmetric shape/intensity templates [@Tustison:2015aa] created from the public MMRR data set  [@landman2011] (cf Figure 2).

### 2016-06-27 results.Rmd
ENH:  More response items.

The resulting rankings for both Stages are given in Figures 4 and 5 where the values for the
separate stages are averaged over the entire corresponding model set.  In addition, we
track the variance for each feature over all models to illustrate the stability of
the chosen features during the evaluation.  This latter information is illustrated as
horizontal errors bars providing the $95^{th}$ percentile
Note that the reader can cross reference Table 1 for identifying corresponding feature types
and names.

@@

Additionally, it is interesting to note some of the other top performing features for Stage 1.
The contralateral difference FLAIR image is  highly discriminative over the set of
evaluation random forest models (see Figure 6).  This accords with the known clinical relevance of
FLAIR images for identifying white matter hyperintensities and the fact that such
pathology does not typically manifest symmetrically in both hemispheres.  Interestingly, the
posterior maps for the deep gray matter are extremely important for accurate white matter
hyperintensity segmentation.  Perhaps the spatial specification of deep
gray matter aids in the removal of false positives.  Inspection of the bottom of the
plots demonstrates the lack of discriminating features associated with the
T1 image which is also well-known in the clinical literature.

@@

As described earlier, for Stage 2, we used the output random forest voting maps from Stage
1 as both features themselves and as priors for input to a Bayesian-based segmentation with
an additional MRF spatial prior.  In Figure 5, the voting maps are labeled as
"_RFStage1VotingMaps_" where the final numeral is associated with the brain
parenchymal labeling given previously.  Similarly, the additional RF prior segmentation
feature probability maps are labeled as "_RFBrainSegmentationPosteriors_".
The Stage 2 feature importance plot follows similar
trends as that for Stage 1 with the T1 images not contributing much to the identification
of white matter hyperintensity voxels.  The initial voting maps from Stage 1 are extremely
important with the top 3 being the estimated locations of the 1) gray matter, 2) white matter, and
3) white matter hyperintensities.  Since these tissue type can be conflated based on intensity
alone it is intuitive that such features would be important.

@@

In Figure 7 are the segmentation comparisons derived from manual segmentations of the same
data.  Despite the large variability characteristic with manual labelings in related fields
[@Grimaud:1996aa;@styner2008;@Garcia-Lorenzo:2013aa], such labelings are characteristic of
current clinical practices and the methodology proposed herein is readily adapted to refinements
in training data.

@@

On the left of Figure 7 are the improvement in Dice values [@tustison2009],
over all white matter hyperintensities when comparing the segmentations between the two stages
where the sum is taken over all individually labeled manual, $T_r$, and automated, $S_r$, lesions and $\cap$
represents the intersection between the manual/automated lesion pair.  Performing
the second round of supervised learning improves these Dice values.  One can also note from the
right side of Figure 6 that the total lesion load volume illustrates a few subjects that are
severe outliers in terms of the number of false positives.  The second round helps to
correct this issue.

>>>>

The resulting rankings for both Stages are given in Figures 5 and 6 where the values for the
separate stages are averaged over the entire corresponding model set.  In addition, we
track the variance for each feature over all models to illustrate the stability of
the chosen features during the evaluation.  This latter information is illustrated as
horizontal errors bars providing the $95^{th}$ percentile
Note that the reader can cross reference Table 1 for identifying corresponding feature types
and names.

@@

Additionally, it is interesting to note some of the other top performing features for Stage 1.
The contralateral difference FLAIR image is  highly discriminative over the set of
evaluation random forest models (see Figure 7).  This accords with the known clinical relevance of
FLAIR images for identifying white matter hyperintensities and the fact that such
pathology does not typically manifest symmetrically in both hemispheres.  Interestingly, the
posterior maps for the deep gray matter are extremely important for accurate white matter
hyperintensity segmentation.  Perhaps the spatial specification of deep
gray matter aids in the removal of false positives.  Inspection of the bottom of the
plots demonstrates the lack of discriminating features associated with the
T1 image which is also well-known in the clinical literature.

@@

As described earlier, for Stage 2, we used the output random forest voting maps from Stage
1 as both features themselves and as priors for input to a Bayesian-based segmentation with
an additional MRF spatial prior.  In Figure 6, the voting maps are labeled as
"_RFStage1VotingMaps_" where the final numeral is associated with the brain
parenchymal labeling given previously.  Similarly, the additional RF prior segmentation
feature probability maps are labeled as "_RFBrainSegmentationPosteriors_".
The Stage 2 feature importance plot follows similar
trends as that for Stage 1 with the T1 images not contributing much to the identification
of white matter hyperintensity voxels.  The initial voting maps from Stage 1 are extremely
important with the top 3 being the estimated locations of the 1) gray matter, 2) white matter, and
3) white matter hyperintensities.  Since these tissue type can be conflated based on intensity
alone it is intuitive that such features would be important.

@@

In Figure 8 are the segmentation comparisons derived from manual segmentations of the same
data.  Despite the large variability characteristic with manual labelings in related fields
[@Grimaud:1996aa;@styner2008;@Garcia-Lorenzo:2013aa], such labelings are characteristic of
current clinical practices and the methodology proposed herein is readily adapted to refinements
in training data.

@@

On the left of Figure 8 are the improvement in Dice values [@tustison2009],
over all white matter hyperintensities when comparing the segmentations between the two stages
where the sum is taken over all individually labeled manual, $T_r$, and automated, $S_r$, lesions and $\cap$
represents the intersection between the manual/automated lesion pair.  Performing
the second round of supervised learning improves these Dice values.  One can also note from the
right side of Figure 7 that the total lesion load volume illustrates a few subjects that are
severe outliers in terms of the number of false positives.  The second round helps to
correct this issue.
